Combined annotation exploration for SCPCP000006

### 2025-03-17 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
clarify that chr text

- the predicted compartment in `fetal_kidney_predicted.compartment` and `fetal_kidney_predicted.compartment.score`
- the predicted cell type in `fetal_kidney_predicted.cell_type` and `fetal_kidney_predicted.cell_type.score`
- the sample identifier in `sample_id`
- the CNV `{dupli|loss}` estimation per chromosome {i} and arm `{p|q}`: `has_{dupli|loss}_chr{i}{p|q}`, in 1 to 22
- the `counts` of [markers genes](https://github.com/AlexsLemonade/OpenScPCA-analysis/tree/main/analyses/cell-type-wilms-tumor-06#the-table-celltype_metadatacsv-contains-the-following-column-and-information)

>>>>

- the predicted compartment in `fetal_kidney_predicted.compartment` and `fetal_kidney_predicted.compartment.score`
- the predicted cell type in `fetal_kidney_predicted.cell_type` and `fetal_kidney_predicted.cell_type.score`
- the sample identifier in `sample_id`
- the CNV `{dupli|loss}` estimate per chromosome `{i}`, where `i \in {1-22}`, and arm `{p|q}`: `has_{dupli|loss}_chr{i}{p|q}`
- the `counts` of [markers genes](https://github.com/AlexsLemonade/OpenScPCA-analysis/tree/main/analyses/cell-type-wilms-tumor-06#the-table-celltype_metadatacsv-contains-the-following-column-and-information)
